### 2013-02-10 doc/xps2013/proposal.tex
started fleshing out my bio

\paragraph{Kahan:} Dr. Kahan's research has focused on parallel computation runtimes, for irregular computation and biological applications.  He is presently an employee of the Department of Energy.  He has no past or current NSF support.

>>>>

\paragraph{Kahan:} Dr. Kahan's research has focused on irregular parallel computation.  Over the course of twelve years, he developed the Tera MTA's multithreaded runtime system and memory allocator still in use today in the Cray XMT, exploring applicability of the system to production codes and benchmarks in the engineering, science, and government domains.  His has been driven by application needs.  The research described herein relies heavily on the experience gained, the innovation being not only to reapply it to mass market technology but also to explore .  He is presently an employee of the Department of Energy.  He has no past or current NSF support.
